\documentclass[17pt]{extarticle}
\usepackage[a4paper, margin=1.7cm]{geometry}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\setmainfont{Garamond Premier Pro}

\date{}

\begin{document}

\section{SHAKE-SPEARES ORACLES}\label{shake-speares-oracles}

\begin{enumerate}
\item
  To swim, to dive into the fire, to ride on the curled clouds,\\Whose
  speechless song being many, seems one.
\item
  Time doth transfix the flourish set on youth,\\Which bounteous gift
  thou shouldst in bounty cherish.
\item
  Be collected; no more amazement. Tell your piteous heart:\\Thou art
  thy mother's glass, and she in thee.
\item
  So, ere you find where light in darkness lies,\\Gentle breath of yours
  my sails must fill.
\item
  Grant, if thou wilt, thou art beloved of many,\\Both in your form and
  nobleness of mind.
\item
  Now my charms are all o'erthrown,\\Begot of nothing but vain fantasy.
\item
  Look, whom she best endow'd she gave thee more;\\Our fancies are more
  giddy and unfirm.
\item
  Sap checked with frost and lusty leaves quite gone,\\Courage and hope
  both teaching him the practice.
\item
  Rough winds do shake the darling buds of May.\\I'll kneel down, and
  ask of thee forgiveness.
\item
  Hourly joys be still upon you!\\And frame your mind to mirth and
  merriment.
\item
  The moon new-bent in heaven, shall behold the night\\That has such
  people in't!
\item
  And having climb'd the steep-up heavenly hill,\\Fortune, good night:
  smile once more: turn thy wheel!
\item
  Beauty o'ersnow'd and bareness every where\\Thaws and resolves itself
  into a dew.
\item
  Their eyes do offices of truth, their words are natural breath,\\All
  dedicated to closeness and the bettering of my mind.
\item
  Sound me from my lowest note to the top of my compass:\\My heart is
  true as steel.
\item
  Thy self thy foe, to thy sweet self too cruel;\\I am sure care's an
  enemy to life.
\item
  Sermons in stones, and good in everything---\\And, therefore, sit you
  down in gentleness.
\item
  Have more than thou showest, speak less than thou knowest,\\Nor lose
  possession of that fair thou ow'st.
\item
  What seest thou else in the dark backward and abysm of time?\\So full
  of shapes is fancy that it alone is high fantastical.
\item
  To give away yourself, keeps yourself still.\\Make me a willow cabin
  at your gate.
\item
  Those be rubies, fairy favors;\\They sparkle still the right
  Promethean fire.
\item
  Men must endure their going hence, even as their coming hither.\\I am
  a fool to weep at what I am glad of.
\item
  Get thee to a nunnery:\\A contract of true love to celebrate.
\item
  If music be the food of love, play on,\\And let this world no longer
  be a stage.
\item
  A man may see how this world goes with no eyes. Look with thine
  ears:\\The murmuring surge, that on the unnumber'd idle pebbles
  chafes.
\item
  And manifest experience had collected\\Of drops that sacred pity hath
  engend'red.
\item
  How beauteous mankind is! O brave new world,\\Merrily, merrily, shall
  I live now.
\item
  These our actors, as I foretold you, were all spirits and\\Do make me
  give the lie to my true sight.
\item
  With the help of your good hands all things in common nature\\Should
  produce without sweat or endeavour.
\item
  And some donation freely to estate\\Under the blossom that hangs on
  the bough.
\item
  Sounds and sweet airs, that give delight and hurt not:\\In a cowslip's
  bell I lie.
\item
  But that the dread of something after death\\It droppeth as the gentle
  rain from heaven.
\item
  And ye that on the sands with printless foot\\Do chase the ebbing
  Neptune---\\O, let me see thee walk! Thou dost not halt.
\item
  But, like a cloistress, she will veiled walk\\Out of the jaws of
  death.
\item
  As there is sense in truth and truth in virtue,\\Joy, gentle friends,
  joy and fresh days of love accompany your hearts!
\item
  For who would bear the whips and scorns of time,\\And kiss the lips of
  unacquainted change?
\item
  Often have you heard that told: Wherefore are these things
  hid?\\Wherefore have these gifts a curtain before 'em?
\item
  And summer's lease hath all too short a date:\\The hour's now come;
  the very minute bids thee ope thine ear.
\item
  I am all the daughters of my father's house, and all the brothers
  too.\\O spirit of love! how quick and fresh art thou.
\item
  And enterprises of great pith and moment\\Are melted into air, into
  thin air.
\item
  O, swear not by the moon, the inconstant moon,\\If it be not now, yet
  it will come: the readiness is all.
\item
  And fearless minds climb soonest unto crowns\\That show, contain and
  nourish all the world.
\item
  Youth's a stuff will not endure;\\Out of that no hope what great hope
  have you!
\item
  And thus the native hue of resolution\\Lies rich in virtue and
  unmingled.
\item
  Happiness courts thee in her best array\\And joy comes well in such a
  needy time.
\item
  Nature's bequest gives nothing but doth lend;\\Thy truth, then, be thy
  dower.
\item
  Study is like the heaven's glorious sun,\\Which touch'd the very
  virtue of compassion in thee.
\item
  Uttering such dulcet and harmonious breath\\That long have frown'd
  upon their enmity!
\item
  Give me your hands, if we be friends;\\We are such stuff as dreams are
  made on.
\item
  And nothing 'gainst Time's scythe can make defence---\\Herein lives
  wisdom, beauty and increase.
\item
  I must go seek some dewdrops here;\\It blesseth him that gives and him
  that takes.
\item
  I put you to the use of your own virtues.\\All things are ready, if
  our minds be so.
\item
  Now stand you on the top of happy hours,\\Against the stormy gusts of
  winter's day.
\item
  Let gentleness my strong enforcement be\\To take a new acquaintance of
  thy mind.
\item
  To take arms against a sea of troubles, and by opposing end them?\\Let
  it not enter in your mind of love.
\item
  These most brisk and giddy-paced times:\\Is man no more than this?
  Consider him well.
\item
  Who with thy saffron wings upon my flowers\\Calls back the lovely
  April of her prime: the form of my intent.
\item
  It is a wise father that knows his own child,\\Like to a double
  cherry, seeming parted, but yet an union in partition.
\item
  In action how like an angel! In apprehension how like a god\\That the
  rude sea grew civil at her song.
\item
  Gaze where you should, and that will clear your sight.\\Enrich the
  time to come with smooth-fac'd peace.
\item
  The slings and arrows of outrageous fortune---\\These blessed candles
  of the night.
\item
  O, from what power hast thou this powerful might,\\By chance or
  nature's changing course untrimm'd?
\item
  Rise from the ground like feathered Mercury,\\Then to the elements be
  free, and fare thou well!
\item
  The constancy and virtue of your love---\\Diffusest honey-drops,
  refreshing showers.
\item
  For never-resting time leads summer on---\\The wheel is come full
  circle: I am here.
\item
  But how is it that this lives in thy mind,\\The undiscover'd country
  from whose bourn no traveller returns?
\item
  They are the books, the arts, the academes---\\And I serve the fairy
  queen.
\item
  Smooth runs the water where the brook is deep.\\What stronger
  breastplate than a heart untainted?
\item
  Then wisely, good sir, weigh our sorrow with our comfort,\\That ebb
  and flow by the moon.
\item
  All that glisters is not gold. To plainness honour's bound\\When
  majesty falls to folly.
\item
  Think'st thou I'd make a life of jealousy?\\The quality of mercy is
  not strain'd.
\item
  O heaven, O earth, bear witness to this sound,\\As full of spirit as
  the month of May.
\item
  When I consider every thing that grows\\Holds in perfection but a
  little moment---\\Pray you, tread softly, that the blind mole may not
  hear a foot fall.
\item
  With gentle conference, soft and affable,\\Let your indulgence set me
  free.
\item
  Light, seeking light, doth light of light beguile;\\Now let not
  Nature's hand keep the wild flood confin'd!
\item
  True, I talk of dreams, for there is nothing\\Either good or bad, but
  thinking makes it so.
\item
  What's in a name? that which we call a rose\\Being once display'd doth
  fall that very hour.
\item
  O, if you but knew how you the purpose cherish!\\If all were minded
  so, the times should cease.
\item
  What is love? 'tis not hereafter,\\And being frank she lends to those
  are free.
\item
  What's to come is still unsure; what's past is prologue.\\Present
  mirth hath present laughter.
\item
  And the moon changes even as your mind,\\But thy eternal summer shall
  not fade.
\item
  I, thus neglecting worldly ends,\\Play out the play.
\item
  Continue still in this so good a mind,\\Wherein it finds a joy above
  the rest.
\item
  To forswear the full stream of the world\\And to live in a nook merely
  monastic\\And by my body's action teach my mind.
\item
  Defer no time, delays have dangerous ends;\\Thou shalt be as free as
  mountain winds.
\item
  Understanding begins to swell by prayer, which pierces so\\That it
  assaults mercy itself, and frees all faults.
\item
  As it is a spare life, look you, it fits my humour well,\\With smiling
  plenty, and fair prosperous days!
\item
  Th'endeavour of this present breath may buy\\The very lifeblood of our
  enterprise.
\item
  But I will tarry; the fool will stay, and let the wise man fly,\\To
  pay this debt of love but to a brother.
\item
  And now let's go hand in hand, not one before another,\\Swifter than
  the moon's sphere.
\item
  Smiling at grief: Awake, awake!\\In delay there lies no plenty.
\item
  And then the moon, like to a silver bow\\Upon the place beneath: it is
  twice blest.
\item
  And as the morning steals upon the night,\\Consideration like an angel
  came.
\item
  When we have shuffled off this mortal coil,\\There's nothing ill can
  dwell in such a temple.
\item
  Be not afeard; the isle is full of noises,\\To entrap the wisest.
\item
  Roses have thorns, and silver fountains mud---\\I would you would make
  use of that good wisdom.
\item
  Make the babbling gossip of the air cry out:\\`There are occasions and
  causes, why and wherefore in all things!'
\item
  Or to thyself at least kind-hearted prove:\\As fast as thou shalt
  wane, so fast thou growest.
\item
  For virtue and true beauty of the soul,\\Halloo your name to the
  reverberate hills!
\item
  But we in silence hold this virtue well:\\The amity that wisdom knits
  not, folly may easily untie.
\item
  Thy virtues spoke of, and thy beauty sounded,\\The better part of
  valour is discretion.
\item
  Draw the curtain close and let us all to meditation,\\To pluck bright
  honour from the pale-fac'd moon.
\item
  My crown is call'd content. A crown it is that seldom kings
  enjoy.\\Silence bestows that virtue on it.
\item
  Time travels in divers paces with divers persons,\\And, since I saw
  thee, th' affliction of my mind amends.
\item
  When wheat is green, when hawthorn buds appear,\\These vacant leaves
  thy mind's imprint will bear.
\item
  Burd'ned with like weight of pain,\\Thou didst smile, infused with a
  fortitude from heaven.
\item
  This bud of love, by summer's ripening breath---\\Was it not to
  refresh the mind of man?
\item
  So shaken as we are, so wan with care---\\Awake, dear heart, awake;
  thou hast slept well. Awake!
\item
  Enforce attention like deep harmony;\\You shall find your safety
  manifested.
\item
  Hath not in nature's mystery more science\\To make the coming hour
  o'erflow with joy?
\item
  How hard it is to hide the sparks of nature!\\Virtue is bold, and
  goodness never fearful.
\item
  I will believe thou hast a mind that suits\\And may enjoy such quiet
  walks as these.
\item
  Who doth ambition shun, and loves to live i' th' sun,\\He finds the
  joys of heaven here on earth.
\item
  Enjoy thy plainness. It nothing ill becomes thee.\\For 'tis the mind
  that makes the body rich.
\item
  Crowning the present, doubting of the rest?\\Keep unshak'd that
  temple, thy fair mind.
\item
  Unlooked for joy in that I honour most:\\Your bounty, virtue, fair
  humility.
\item
  Divert strong minds to the course of alt'ring things.\\Where words are
  scarce, they are seldom spent in vain.
\item
  For virtue's office never breaks men's troth,\\Nor hath Love's mind of
  any judgment taste.
\item
  As Nature was in making graces dear,\\Then happy I that love and am
  beloved.
\item
  You bear a gentle mind, and heav'nly blessings follow such
  creatures.\\Steel thy fearful thoughts and change misdoubt to
  resolution.
\item
  Do not infest your mind with beating on\\The strangeness of this
  business;\\It is the purpose that makes strong the vow.
\item
  A turn or two I'll walk to still my beating mind.\\My crown is in my
  heart, not on my head.
\item
  That love which virtue begs and virtue grants\\Is true of mind and
  made of no such baseness.
\item
  Your patience and your virtue well deserves it\\That every eye which
  in this forest looks\\Shall see thy virtue witness'd every where.
\item
  Cease, cease these jars and rest your minds in peace\\And take thou my
  oblation, poor but free.
\item
  To make you understand this in a manifested effect:\\Now you are heir,
  therefore enjoy it now.
\item
  The purest spring is not so free from mud;\\It is the show and seal of
  nature's truth.
\item
  Comets, importing change of times and states---\\O infinite virtue,
  com'st thou smiling from\\The world's great snare uncaught?
\item
  The very virtue of compassion in thee\\Shall change all griefs and
  quarrels into love.
\item
  You see how all conditions, how all minds tender down their
  services?\\Silence is the perfectest herald of joy.
\item
  All of one nature, of one substance bred,\\When inward joy enforc'd my
  heart to smile!
\item
  Who alone suffers suffers most i' th' mind,\\Then music with her
  silver sound\\With speedy help doth lend redress.
\item
  An odorous chaplet of sweet summer buds\\Whereof the root was fix'd in
  virtue's ground.
\item
  One feast, one house, one mutual happiness,\\With profits of the mind,
  study and fast.
\item
  The griefs are ended by seeing the worst,\\Then sigh not so, but let
  them go.
\item
  To shun the heaven that leads men to this hell,\\The wild sea of my
  conscience, I did steer.
\item
  Through the forest I have gone\\To make some special instance
  special-blest.
\item
  Clouds and eclipses stain both moon and sun---\\I'll be as patient as
  a gentle stream.
\item
  For I must tell you friendly in your ear:\\The forest walks are wide
  and spacious.
\item
  As plays the sun upon the glassy streams,\\Awake the pert and nimble
  spirit of mirth.
\item
  Full merrily the humble-bee doth sing,\\`The more I give to thee, the
  more I have.'
\item
  The sea all water, yet receives rain still---\\God be thank'd, there
  is no need of me.
\item
  Out of this nettle, danger, we pluck this flower, safety,\\And make us
  heirs of all eternity.
\item
  That's a valiant flea that dare eat his breakfast on the lip of a
  lion.\\Whilst I am bound to wonder, I am bound to pity too.
\item
  Full many a glorious morning have I seen,\\For I impair not beauty
  being mute.
\item
  A little fire is quickly trodden out;\\All losses are restored, and
  sorrows end.
\item
  My friends were poor, but honest; so's my love.\\In life's uncertain
  voyage, I will some kindness do them.
\item
  Let's take the instant by the forward top\\And do whate'er thou wilt
  swift-footed Time.
\item
  One minute, nay, one quiet breath of rest.\\A kingdom for it was too
  small a bound.
\item
  With sun and moon, with earth and sea's rich gems,\\Buy terms divine
  in selling hours of dross.
\item
  Sweet are the uses of adversity\\Over whose acres walk'd those blessed
  feet.
\item
  Men of great worth resorted to this forest\\As many fresh streams meet
  in one salt sea.
\end{enumerate}

\end{document}
